Dimensions of the impacts of land transitions in the Amazon and Cerrado

### 2023-02-07 manuscript/lct_se_ac.qmd
Start introduction.

@@

1.  Predict probability and area of native vegetation suppression in the Amazon and Cerrado;
    a.  What are the main drivers of native vegetation suppression?
    b.  How do drivers interact among them?
2.  Predict land cover transition trajectories after native vegetation suppression;
    a.  What are the main drivers of land cover dynamics after native vegetation suppression?
    b.  How do drivers interact among them?
    c.  What are the main patterns for future projections in the Amazon and Cerrado?
3.  Predict the impact of land cover transitions over environmental and social variables;
    a.  What is the importance of land cover transitions in predicting environmental and social variables?
    b.  Does land-use transitions interact with other drivers of environmental and social variables?
    c.  What are the expected social and environmental projections in different land-cover trajectories for the near future?

>>>>

Analysis of the drivers and impacts of native vegetation suppression in Brazil is not new. However, the approaches used to analyse this phenomena usually focus in few dimensions. I propose creating a modelling framework, using modern techniques, to predict and explain native vegetation suppression and its impacts on social and environmental variables. The study will also analyse the Amazon and Cerrado at the same time, and will explore whether predictions from one biome are related to predictions from the other biome.

@@

1.  Predict probability and area of native vegetation suppression in the Amazon and Cerrado;
    a.  What are the main drivers of native vegetation suppression?
    b.  How do drivers interact among them?
2.  Predict land cover transition trajectories after native vegetation suppression;
    a.  What are the main drivers of land cover dynamics after native vegetation suppression?
    b.  How do drivers interact among them?
    c.  What are the main patterns for future projections in the Amazon and Cerrado?
3.  Predict the impact of land cover transitions over environmental and social variables;
    a.  What is the importance of land cover transitions in predicting environmental and social variables?
    b.  Does land-use transitions interact with other drivers of environmental and social variables?
    c.  What are the expected social and environmental projections in different land-cover trajectories for the near future?
    d.  Do predictions from both biomes show relation between each other?
